\todo[inline]{Level names need to be verified}

\newpage
\section{Earth}
\todo[inline,color=green]{There are plans to remake all tutorial missions, especially first mission on Earth}

The survival of mankind on earth is jeopardized by an imminent ecological collapse: Earth is only sand and fog. Three training missions take place on earth, in order to know the basic elements and to master the interface.


\subsection{Equipment}

The hero must just walk around in order to find his space pack, that will stay on his back until the end of the game: it contains oxygen and a jet engine to allow him to fly (only from moon on; in some missions, flight is impossible or limited due to damage or too high temperatures).


\subsection{Construction}

Learn to use the fundamental technology that you will use on you whole trip: build buildings with titanium, a raw material available on all planets, even on foreign solar systems.


\subsection{Take-off}

Take a glimpse into a fundamental problem: making bots move. At this stage, there are only wheeled and tracked bots, but their respective characteristics and weak points already become obvious. Take the black box on a near-by mountain, put it on your spaceship, and take off to meet adventure.


\newpage
\section{Moon}

The stop on the moon is still part of the training phase of the expedition. Do the necessary research to be able to build flying bots, learn how to control them, and take a glimpse to the first raw material supply problems.


\subsection{Flight on the Moon}

Build some flying bots (after having done the necessary research) and use them to take some titanium ore in steep craters.


\subsection{Flight Training 1}

Training with winged bots.


\subsection{Flight Training 2}

One more training with winged bots.


\subsection{Black Box}

Use a radar and a map in order to find the black box left by the first expedition.


\newpage
\section{Tropica}

On Tropica, you face for the first time hostile aliens, progressively you must develop the necessary technology and skill to fight against them.


\subsection{The Trap}

The missions looks so easy: Just go to the end of a deep valley, and bring a box filled with a new explosive (developed by the first expedition) back to the space ship. However, when you arrive close to the box, there are many giant ants that you did not even see at first sight. They shoot some green poison, you ''die'', and the mission is failed.


\subsection{Amnesic}

The failure in the previous mission does not prevent you from getting to the next mission. Houston is worried about what happened, your equipment is partly lost or damaged, and you do not even know where you are. First of all, try to find your way back to your spaceship.


\subsection{Assault}

Now that the aliens are identified, it becomes urgent to build some weapons that will allow you to defend yourself against the aliens. Then you can start to clean the region from these awful beasts that made you suffer so badly, using a winged shooter and a radar.


\subsection{Shooting training}

Winged shooters (flying bots equipped with a gun) are not easy to pilot. With an installation set up by the first expedition to check the efficiency of programmed robots, improve your skill at the controls of winged shooters.


\subsection{Black Box}

As on every planet before and after, you must get the black box left by the first expedition. This time, it lays deep in the water. Build a submarine, and get it.


\newpage
\section{Crystalium}

Crystalium is an ice-cold and naked planet, with mainly technical missions. The player gets his first in-depth glimpse into programming, and learns about some technologies that were not used before: sniffer bots (detect raw materials in the underground), derricks (extract them) and defense towers (shoot automatically on aliens that come too close). Even a new kind of aliens is ''technical'': this kind of worm does no harm, but injects some viruses into the computer programs of machines and bots...


\subsection{Radar and Virus}

You must build a radar station on top of a mountain crawling with a strange kind of "virus worm". Do some research to build a defense tower, that will clean up the worms: they were probably responsible for the transmission problems with the first expedition. To ease your work with raw material supply, Houston transmitted a program that makes wheeled grabbers collect titanium ore. The program is a very simple one, and is fully commented and explained. Just use it, or try to understand it: you can choose.


\subsection{Clean up the Worms}

The mission, cleaning up the worms, is only a pretext to showing the fundamentals of mining technology: a sniffer bot sounds the underground and detects titanium ore, uranium ore and energy. The fact that vital titanium ore will be found on another island justifies a further development of the program that collects titanium: in order to prevent the loss of a winged grabber if the power cell runs out of energy when flying over water, the bot will recharge the cell automatically. Only after some infrastructure work, the player can turn to action: once he built a winged shooter, he can shoot all the worms.


\subsection{Catch the Thief}

A robot left over by the first expedition takes the black box from the spaceship and flies away with it. Try by any means to get the black box back. Houston promises to investigate the causes of this incident (but will never find out).


\subsection{The Lost Valley}

In a valley full of fog, try to find the black box from the first expedition. Even the satellite can not tell you what problems you could meet. You will actually meet many ants... Only fast mouse handling can save you.


\newpage
\section{Saari}

Saari is a very hot desert planet; also fighting will be hot. Most missions have got to do with shooting, or with killing ants without shooting.


\subsection{Uranium}

The first contact with nuclear material is only a pretext to killing all ants that keep the mountain where you can find the uranium ore. These ants look so easy to shoot, but the player will get a surprise...


\subsection{Invasion}

Houston was wrong, and made the spaceship land almost in the middle of an ant hill... But Houston has got also a program ready that will help the player win some time, until he manages to build his own defense structure.


\subsection{Shrewed}

The ants in this mission really do not look aggressive; they are even afraid of the cosmonaut. But Houston says you must kill them all, though you have not even a robot to help you in this task.


\newpage
\section{Volcano}

Volcano is a planet with high volcanic activity. The ambient temperature is so high that flying is impossible in most places. Two new technologies appear on this planet -- nuclear power cells, that give bots a much larger autonomy, and legged bots -- these are born from an integration of alien technology, and turn out to be highly efficient and economic. The first expedition left behind much infrastructure, so building activity is reduced to the benefit of research
and action.


\subsection{Transportation}

In order to achieve the mission (take a box of explosive to the spaceship), the player must develop nuclear energy. A new program sent by Houston makes bots taking care of raw material supply much more autonomous, with all the problems that could arise from this autonomy... Some ugly spiders will make your life a little more difficult.


\subsection{Analysis}

Take some ''organic matter'' from the ants, and feed your laboratory with it: we can learn a lot from alien
organisms. Of course ants will not give their technology away without a fight, and the symbiosis of ants and
wasps proves highly efficient in keeping intruders out.


\subsection{Climbing}

Use the new legged bots to bring back the black box from the first expedition.


\subsection{Rescue Operation}

You were just taking off when the satellite detected a bot of a new type. Just go and bring it back.


\subsection{Get Back}

The new bot is on the spaceship: it carries a new weapon system, called ''orgaball gun'', that is much more economic than the traditional fireball gun. You just have to get back to the spaceship too. Or rather say: you just have to fight your way back.


\subsection{Help!}

You and the bot are on the ship; a last fight, and you can take off.


\newpage
\section{Centaury}

Centaury is a planet where not much is left from the first expedition, so raw material and energy supply are one of your main tasks. Political considerations start to influence your mission: the American Congress and world public opinion do not agree with some methods that Houston apply.


\subsection{Discovery}

The orgaball gun made by the first expedition and left on Volcano proved very efficient. To elaborate the plans necessary to produce new ones, you must again get some of this ''organic matter'' produced by the ants. But first, you must solve the energy and raw material supply problems, that are complicated by the fact that the first expedition left over so little, and the few remnants are scattered over the whole region.


\subsection{Shooting Training}

On the last missions on Volcano, your skills at the controls of shooter bots were insufficient. A little training seems necessary.


\subsection{Purification}

The radar station built on Centaury by the first expedition was destroyed by aliens. This was the reason for the interruption of communication. Build a new radar station, and make sure that it will not be destroyed...


\subsection{Best Greetings}

You must get the black box of the first expedition. But there are so many ants keeping it, and you have got so little energy left… Fortunately, some information left behind by the first expedition tells us about a new weapon system that renders all ants inside a certain range harmless for some while. Activate your research center, and you will know if and how it works. This new weapon system is valuable also for political reasons: the Congress and public opinion do not appreciate the repeated ''massacres'' among the ''native population'' that remember colonization in former centuries. You will have to restrain your shooting activity...


\subsection{Retaliation}

Just when you wanted to take off, a group of very aggressive ants attacked. Hopefully the Congress will accept that you used your attack weapon systems in a case of self-defense.


\newpage
\section{Orpheon}

Orpheon might be the visually most stunning planet that you ever saw, survival on it is awfully difficult: not only aliens are more aggressive and more numerous than anywhere else, even Nature manages to destroy your bots and buildings.


\subsection{Stronghold}

Also on this planet, the radar built by the first expedition was destroyed, for reasons that quickly become obvious: aliens are numerous, and electromagnetic activity in the atmosphere produces lightening that destroys very soon every building or bot that is not protected by lightening conductors. The frequent lightening has also good sides: lightening conductors can recharge power cells, and are the only available energy on this planet. Renewable energies enter the game. The problem of the aliens that will attack the new radar station is more difficult to solve: you can not anymore slaughter them all, as you did in previous missions. The only ''politically correct'' way is to protect the radar station with defense towers that kill only aliens that threaten directly this vital installation. The problem of limited cell capacity can be solved thanks to programming: programmed bots take the empty cells, recharge them under the lightening conductor and put them back on the defense towers.


\subsection{Shelter}

The black box of the first expedition is only one hundred yards away, but lightening is more frequent than before... Here again, programming is needed: only a programmed winged shooter can replace the defense towers that can not be built fast enough to defend against the first alien assault.


\newpage
\section{Terranova}

Terranova is the final destination of the expedition: all characteristics of the planet seem to fit to a large scale colonization. So it becomes more important than ever to take care of the ecosystem. However, some ants are so aggressive that you can hardly imagine living with them forever. Houston kept its promise and sent some information about a new defensive weapon system: they say it works like a ''shield''. Shooting will be replaced by shielding. The first expedition left a last gift for us: The message they left says that it is a new weapon system, the only one to be able to ''kill the Big Lady'', but they could not use it before everything went wrong. This new weapon system is hidden away in a vault, so just find the four keys that you need to open it...


\subsection{The First Key}

Houston transmitted information about the ''shielder'', a new defensive weapons system. Perform the necessary research, and you can go and take the first key... Or better, add a little programming: unless you can control two bots at the same time, you will not be able to get through the dangerous passages fast enough. Just program the shielder in such a way that it finds alone the way through the passage, and follow it...


\subsection{The Second Key}

The submarine bot (called ''subber'') that you took with you at the end of the previous mission will prove valuable when you must take the second key at the bottom of a lake. Do not care about all the ants that attack you: just hurry up before the cell of the shielder is empty.


\subsection{The Third Key}

The third key is hidden somewhere in the underground, ''where the mushrooms grow''. You can start to look for it if you survive to the last alien attack of the game. Legged bots will prove helpful in a region where winged bots can not pass the high mountain ranges.


\subsection{The Forth Key}

The fourth key is easy to find, and with it you can finally gain access to the new weapons system that the first expedition left behind because they had no chance to use it. There are too many aggressive ants in this region. The first expedition developed the new weapon system precisely for killing the alien queen that lays the eggs where all the aggressive ants come out... The Congress talked for hours and days, and finally allowed the ''aggressive'' queen to be killed. Once this is done, purely defensive weapon systems will allow mankind to live on this new planet together with the original aliens.